\documentclass[11pt]{article}
\usepackage[noBBpl]{mathpazo}

%\documentclass[12pt]{article}
%\usepackage{mathptmx}

\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{microtype}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cancel}
\usepackage{mathrsfs}
\input xy
\xyoption{all}

\usepackage[noend]{algorithmic}
\usepackage{listings}
\lstset{language=Java, tabsize=4}

%\renewcommand{\labelenumi}{\textbf{(\arabic{enumi})}}

\pdfpagewidth 8.5in
\pdfpageheight 11in
\topmargin 0in
\headheight 0in
\headsep 0in
\textheight 9in
\oddsidemargin 0in
\evensidemargin 0in
\textwidth 6.5in

\theoremstyle{plain}
\newtheorem*{theorem}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{prop}{Proposition}
\newtheorem*{cor}{Corollary}

\theoremstyle{definition}
\newtheorem*{defn}{Definition}
\newtheorem*{prob}{Problem}
\newtheorem*{ex}{Example}
\newtheorem*{exes}{Examples}

\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{note}{Note}
\newtheorem*{claim}{Claim}
\newtheorem*{case}{Case}
\newtheorem*{conclusion}{Conclusion}

\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Q}{\mathbb Q}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}

\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\abs}[1]{{\left\lvert{#1}\right\rvert}}
\newcommand{\norm}[1]{{\left\lVert{#1}\right\rVert}}
\newcommand{\inner}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\floor}[1]{{\left\lfloor{#1}\right\rfloor}}
\newcommand{\ceil}[1]{{\left\lceil{#1}\right\rceil}}
\newcommand{\pd}[2]{{\frac{\partial{#1}}{\partial{#2}}}}
\newcommand{\unit}[1]{\,\mathrm{#1}}
\newcommand{\e}[1]{\times10^{#1}}
\newcommand{\bra}[1]{\langle #1 \rvert}
\newcommand{\ket}[1]{\lvert #1 \rangle}
\newcommand{\braket}[2]{\langle #1 | #2 \rangle}
\newcommand{\braaket}[3]{\bra{#1}#2\ket{#3}}

\DeclareMathOperator{\Real}{Re}
\DeclareMathOperator{\Imag}{Im}

\newcommand{\newproblem}[1]{\section*{\textsf{#1}\smallskip\hrule}}

\begin{document}
\begin{center}
\section*{How to create a standalone program}
\end{center}
\section*{Introduction}
Eclipse can produce standalone Java programs called JAR files (for Java
ARchive). As long as your computer has a Java Runtine Environment (JRE)
installed, you should be able to run a .jar as a program by double-clicking it.
Normally, this is very easy to do with a few clicks, but because we're using the
non-standard ACM libraries and the Stanford plugin in the ConsolePrograms and
GraphicsPrograms we have been writing throughout the course, we have to go
through a fairly long process instead. Here are the steps required to produce a
standalone program.
\section{Adding a {\tt main()} method}
You may have wondered why we needed a {\tt main()} method in the LeJOS programs
but not in the ConsolePrograms and GraphicsPrograms. This is because the
Stanford Eclipse plugin is automatically adding a {\tt main()} method. Before we
can export to a JAR, we need to add this method back in. That is, inside your
main class (the one that extends ConsoleProgram or GraphicsProgram), you shoudld
add the code:
\begin{lstlisting}
public static void main(String[] args) {
   new MyClass().start(args);
}
\end{lstlisting}
In this code snippet, you should replace ``MyClass'' with whatever the name of
your class is. So for instance if at the top of your file you have the line
\begin{lstlisting}
public class RandomCircles extends GraphicsProgram {
\end{lstlisting}
then you should write RandomCircles in place of MyClass in the above code. 
\section{Using Eclipse's Export Wizard}
The next series of steps will be to use Eclipse's Export Wizard feature to
produce a JAR and a manifest file. We will later need to modify the manifest
file to specify that the ACM libraries should be included, but first perform the
following steps:
\begin{enumerate}
  \item Select the project you want to export in the left-hand pane (the
    ``Package Explorer''). At the top of the screen, go to the {\bf File} menu
    and select {\bf Export}. This should make an export window appear in the
    middle of the screen.
  \item On the ``choose export destination'' screen, select the {\bf Java}
    folder, and then select the option {\bf JAR file}. Click the {\bf Next}
    button.
  \item On the ``JAR File Specification'' screen, check the box next to the name
    of your project in the left-hand box, and then select the location you want
    the JAR file saved to in the box labeled ``Select the export destination.''
    Then click {\bf Next}.
  \item The next screen is ``JAR Packaging Options.'' This screen is not
    important for us, and you can simply click {\bf Next} without changing
    anything.
  \item The next screen is ``JAR Manifest Specification,'' and requires several
    steps.
    \begin{itemize}
      \item First, near the bottom of the window, select the main class using
        the {\bf Browse} button.  The main class is the one to which we earlier
        added the {\tt main()} method in the first step above.
      \item Then click the radio button labelled ``Generate the manifest file.''
      \item Then check the box for ``Save the manifest in the workspace.''
      \item Then click {\bf Browse} next to the box for ``Manifest file,''
        navigate to the folder where your project exists, and enter ``manifest''
        as the file name. If you do this correctly, the box will likely be
        filled with something like ``/ProjectName/manifest''.
      \item Finally, click {\bf Next}.
    \end{itemize}
\end{enumerate}
After all of these steps, you should see the manifest file show up in the
package explorer under the current project.
\section{Editing the manifest file}
We need to edit the manifest file that was just created to tell it to use the
ACM libraries. Open up the manifest file which should have just appeared in your
project folder, and add the line 
\begin{quote}
  Class-Path: acm.jar
\end{quote}
After doing so, the manifest file should appear something like
\begin{quote}
  Manifest-Version: 1.0 \\
  Main-Class: MyClass \\
  Class-Path: acm.jar
\end{quote}
Make sure you save the manifest file after changing it.
\section{Export Wizard again}
Now repeat the process described in the secion titled ``Using Eclipse's Export
Wizard'' up until just before step 5. This time, on the screen labelled ``JAR
Manifest Specification,'' you should check the radio button for ``Use existing
manifest from workspace,'' and use the {\bf Browse} button to select the
manifest file you just created.

Click {\bf Finish}. If Eclipse asks you if you want to overwrite the old .jar
file, saw yes. We're almost there!
\section{Distributing the .jar file}
Now you have a .jar file containing your code, but you can't just send it to
your friends because they won't have the ACM library. To run your program, you
will need to have your .jar plus {\tt acm.jar} in the same directory, and then
you can just double-click on your .jar to start your application.

Note that if your application requires any auxiliary files, such as images, you
will also need to put them in the same directory with your .jar and {\tt
acm.jar}.

If you want to send your application to friends, the easiest way is probably to
put all the required files together into a folder, and then compress that folder
into a .zip and send it.
\end{document}
